---
title: "Vignette Title"
author: "Author Name" <email@domain.com>
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
bibliography: bibliography.bib
tags:
license: Creative Commons Attribution-ShareAlike 4.0 International
---

```{r, pkgs, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(FLCore)
# LOAD other packages, including FLPKG, here
```

# Introduction

[@FLR_KellMG2007]

# Background / Methods

# Using the FLPKG package

## Example / Workflow 1

## Example / Workflow 2

# More information

* You can submit bug reports, questions or suggestions on `FLPKG` at the `FLPKG` issue page ^[<https://github.com/flr/FLPKG/issues>], or on the *FLR* mailing list.
* Or send a pull request to <https://github.com/flr/FLPKG/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage ^[<http://flr-project.org>].
* The latest version of `FLPKG` can always be installed using the `devtools` package, by calling
```{r, devtools, echo=TRUE, eval=FALSE}
	library(devtools)
	install_github('flr/FLPKG')
```

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLPKG: `r packageVersion('FLPKG')`
* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

## Author information

**Name SURNAME**. Affiliation. Address, Locality (RE) Country.

# References
